### 2021-01-04 tex/paper.tex
Fix spelling.

Similar to Oracle APEX and Simplifier, Mendix is also a web-based environment for low-code application development. Mendix offerse a free tier which allows hosting unlimited applications with 1GB of memory and 0.5GB of storage per application. For more advanced needs, Mendix offers an enterprise option starting at 1875€ per month, allowing on-premises hosting and hosting on private clouds, e.g. AWS, IBM etc. For our evaluation purposes, the free tier is more than enough given there are no restrictions on the provided functionality. Creating an account was straight-forward and we were able to log in within minutes of registering. There are two options for developing applications using Mendix: The first is the web-based environment called Mendix Studio, the second a native desktop application called Mendix Studio Pro, offering more advanced options for professional users. Unfortunately Mendix Studio Pro is only available for Microsoft Windows, so we were not able to test it, the basic functionality for creating low-code application is the same in both versions of Mendix Studio, however.

@@

In \cref{fig:corteza_home_screen}, we can see the initial screen of the Corteza platform. By selecting “Low Code”, we reach a new view containing all existing “Low Code Namespaces”. A namespace can be thought of as an individual application within the low-code environment. In order to start with our application, we create a \texttt{todo-list} namespace. Next we need to create a module. A module in Corteza is similar to creating a database schema for a single table. For our application, we create a module containing text fields for \texttt{title} and \texttt{body} and a drop-down field for the \texttt{status}. We also mark \texttt{title} as a required field, as seen in \cref{fig:corteza_module}. Next, we need to create a page which lets us add TODOs to our list. To do this, we create a blank page and add the pre-built “Record List” block. In the “Record List” block, we select our “Todo Module” as the data source and select all fields so they are displayed in the list. The list also provides an option to allow inline editing of records. Without this option, the user has to click on the list item to open the detail page in order to edit it. Unfortunately, for some reason when enabling the checkbox to allow inline editing, we were unable to save the page with this configuration. Nevertheless, the basic functionality of our application was completely implemented in less than ten minutes.

@@

For our todo list, we created a new application called “TODO List”. The setup wizard allows customising the color theme of the application, the menu style (e.g. side menu or top menu), language as well as the application icon. Once created, we had a blank application containing a login page and a home page. The next thing we needed to do was set up a database table for our todo items. Basic SQL knowledge is required to do this since properly setting up a primary key and a unique constraint for it is necessary to be able to insert data later on. We now had a \texttt{TODOS} table containing \texttt{ID}, \texttt{STATUS}, \texttt{TITLE} and \texttt{BODY} and were now able to add a new page to our application.

@@

There are many different page styles to choose from, as seen in \cref{fig:oracle_apex_create_page}. For our use case, we chose the “Form” page template. The user simply assigns a page name and subsequently selects the  corresponding database table. The result is a form page with all fields of the database table which lets the user add new tasks and edit existing ones. Some minor visual adjustments were necessary for the form page, i.e. hiding the automatically generated \texttt{ID} and setting the \texttt{STATUS} to “outstanding” by default when adding a new task. The next step was to create a list containing our todo items with a button that opens the form page to add new ones. Similar to the page templates, there are many different building blocks to choose from. We used the same as the one used in the sample application, the “Interactive Report”, a table view with filtering options. Lastly, we added a \texttt{CREATE} button to the top of this component, linking it to the form page created earlier.

>>>>

Similar to Oracle APEX and Simplifier, Mendix is also a web-based environment for low-code application development. Mendix offers a free tier which allows hosting unlimited applications with 1GB of memory and 0.5GB of storage per application. For more advanced needs, Mendix offers an enterprise option starting at 1875€ per month, allowing on-premises hosting and hosting on private clouds, e.g. AWS, IBM etc. For our evaluation purposes, the free tier is more than enough given there are no restrictions on the provided functionality. Creating an account was straight-forward and we were able to log in within minutes of registering. There are two options for developing applications using Mendix: The first is the web-based environment called Mendix Studio, the second a native desktop application called Mendix Studio Pro, offering more advanced options for professional users. Unfortunately Mendix Studio Pro is only available for Microsoft Windows, so we were not able to test it, the basic functionality for creating low-code application is the same in both versions of Mendix Studio, however.

@@

In \cref{fig:corteza_home_screen}, we can see the initial screen of the Corteza platform. By selecting “Low Code”, we reach a new view containing all existing “Low Code Namespaces”. A namespace can be thought of as an individual application within the low-code environment. In order to start with our application, we create a \texttt{todo-list} namespace. Next we need to create a module. A module in Corteza is similar to creating a database schema for a single table. For our application, we create a module containing text fields for \texttt{title} and \texttt{body} and a drop-down field for the \texttt{status}. We also mark \texttt{title} as a required field, as seen in \cref{fig:corteza_module}. Next, we need to create a page which lets us add TODOs to our list. To do this, we create a blank page and add the pre-built “Record List” block. In the “Record List” block, we select our “TODO Module” as the data source and select all fields so they are displayed in the list. The list also provides an option to allow inline editing of records. Without this option, the user has to click on the list item to open the detail page in order to edit it. Unfortunately, for some reason when enabling the checkbox to allow inline editing, we were unable to save the page with this configuration. Nevertheless, the basic functionality of our application was completely implemented in less than ten minutes.

@@

For our TODO list, we created a new application called “TODO List”. The setup wizard allows customising the colour theme of the application, the menu style (e.g. side menu or top menu), language as well as the application icon. Once created, we had a blank application containing a login page and a home page. The next thing we needed to do was set up a database table for our TODO items. Basic SQL knowledge is required to do this since properly setting up a primary key and a unique constraint for it is necessary to be able to insert data later on. We now had a \texttt{TODOS} table containing \texttt{ID}, \texttt{STATUS}, \texttt{TITLE} and \texttt{BODY} and were now able to add a new page to our application.

@@

There are many different page styles to choose from, as seen in \cref{fig:oracle_apex_create_page}. For our use case, we chose the “Form” page template. The user simply assigns a page name and subsequently selects the  corresponding database table. The result is a form page with all fields of the database table which lets the user add new tasks and edit existing ones. Some minor visual adjustments were necessary for the form page, i.e. hiding the automatically generated \texttt{ID} and setting the \texttt{STATUS} to “outstanding” by default when adding a new task. The next step was to create a list containing our TODO items with a button that opens the form page to add new ones. Similar to the page templates, there are many different building blocks to choose from. We used the same as the one used in the sample application, the “Interactive Report”, a table view with filtering options. Lastly, we added a \texttt{CREATE} button to the top of this component, linking it to the form page created earlier.
